---
title: "615FinalProject"
author: "Kaiyu Yan"
date: "December 11, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,echo=FALSE,warning=FALSE,comment=FALSE,message=FALSE}
if (!require(tidyverse)) install.packages('tidyverse')
library(tidyverse)
if (!require(ggplot2)) install.packages('ggplot2')
library(ggplot2)
if (!require(plotly)) install.packages('plotly')
library(plotly)
if (!require(scales)) install.packages('scales')
library(scales)
if (!require(zipcode)) install.packages('zipcode')
library(zipcode)
if (!require(devtools)) install.packages('devtools')
library(devtools)
if (!require(mapdata)) install.packages('mapdata')
library(mapdata)
if (!require(ggmap)) install.packages('ggmap')
library(ggmap)
if (!require(benford.analysis)) install.packages('benford.analysis')
library(benford.analysis)
if (!require(leaflet)) install.packages('leaflet')
library(leaflet)
if (!require(knitr)) install.packages('knitr')
library(knitr)
if (!require(png)) install.packages('png')
library(png)
```
# Introduction

For this project, I'm investigarte dataset and trying to determine if it was fabricated or altered in some way. 

###Description of data
The data is NYC Manhattan property sale in year 2017 that obtained from NYC Department of Finance https://www1.nyc.gov/site/finance/taxes/property-annualized-sales-update.page. The data include the following useful variables for our future analysis:

1)NEIGHBORHOOD.

2)BUILDING CLASS CATEGORY.

3)BUILDING CLASS AT TIME OF SALE. 

4)ZIPCODE.

5)LAND SQUARE FEET.

6)GROSS SQUARE FEET.

7)YEAR BUILT.

8)SALE PRICE.

9)SALE DATE.

The interesting variable I am using in the dataset are Sale price,neighborhood, land and gross square feet, and sale date.

For Benford analysis, I will analyze the sale price and see if the price was faked or not. 

# EDA

### Data Import and Cleaning
```{r}
Manhattan <- read.csv("2017_manhattan.csv") %>% 
  select(2,9,11,12,13,15,16,17,19,20,21)
```

```{r,echo=FALSE,warning=FALSE,comment=FALSE}
### Convert data format into correct format
Manhattan$SALE.PRICE. <- as.numeric(gsub(",","",as.character(Manhattan$SALE.PRICE.),fixed=TRUE)) #Convert format to numeric for price 
Manhattan$LAND.SQUARE.FEET. <- as.numeric(gsub(",","",as.character(Manhattan$LAND.SQUARE.FEET.),fixed=TRUE))#Convert format to numeric for land sqft
Manhattan$GROSS.SQUARE.FEET. <- as.numeric(gsub(",","",as.character(Manhattan$GROSS.SQUARE.FEET.),fixed=TRUE))#Convert format to numeric for gross sqft
Manhattan$SALE.DATE. <- as.Date(Manhattan$SALE.DATE.,"%m/%d/%Y")#conver date format

#Create a new column indicate Sale Month
 M <- data.frame(Manhattan$SALE.DATE.,
            year = as.numeric(format(Manhattan$SALE.DATE., format = "%Y")),
            month = as.numeric(format(Manhattan$SALE.DATE., format = "%m")),
          day = as.numeric(format(Manhattan$SALE.DATE., format = "%d"))) %>% 
   select(3)
Manhattan <- cbind(Manhattan,M)
colnames(Manhattan)[12] <- "Month"
Manhattan$Month <- month.abb[Manhattan$Month]

#convert format
Manhattan <- filter(Manhattan,YEAR.BUILT.>1800)
Manhattan$YEAR.BUILT.  <- ifelse(Manhattan$YEAR.BUILT.  == "0", NA, Manhattan$YEAR.BUILT) 
Manhattan$YEAR.BUILT. <- as.Date(as.character(Manhattan$YEAR.BUILT.), format = "%Y")
Manhattan$ZIP.CODE. <- as.character(Manhattan$ZIP.CODE.)
Manhattan$BUILDING.CLASS.AT.TIME.OF.SALE. <- as.character(Manhattan$BUILDING.CLASS.AT.TIME.OF.SALE.)
Manhattan$RESIDENTIAL.UNITS. <- as.numeric(as.character(Manhattan$RESIDENTIAL.UNITS.))

#Filter neighborhoods in midtown area
Midtown <- filter(Manhattan,str_detect(Manhattan$NEIGHBORHOOD., "MIDTOWN"))
```



```{r}
ggplot(Manhattan)+
   geom_bar(mapping = aes(x = NEIGHBORHOOD.))+
   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  ggtitle("Property Sales Count Based on Location ")
```

```{r}
ggplot(Manhattan)+
   geom_bar(mapping = aes(x = Month))+
   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  ggtitle("Property Sales Count Based on Location ")
```

```{r}
A <- ggplot(Midtown,aes(NEIGHBORHOOD., fill =BUILDING.CLASS.AT.TIME.OF.SALE.)) +
        geom_bar(position = "fill") +
      
        xlab ("Categories") +
        ylab("Percentage") + 
        theme(axis.text.x = element_text(size = 12, angle =45, hjust = 1)) + 
        guides(fill=guide_legend(title="Answers"))+
  ggtitle("Midtown Sale's Building Class")
A
```

```{r}
ggplot(data = Manhattan,
  aes(Month, SALE.PRICE.)) +
  stat_summary(fun.y = sum, # adds up all observations for the month
    geom = "bar") + # or "line"
  # custom x-axis labels
   scale_y_continuous(labels = comma)+
 theme(axis.text.x = element_text(angle =60, hjust = 1))+
  ggtitle("Total Sales Price Per Month")
```

```{r}
ggplot(data = Manhattan,
  aes(NEIGHBORHOOD., SALE.PRICE.)) +
  scale_y_continuous(labels = comma)+
  stat_summary(fun.y = sum, # adds up all observations for the month
    geom = "bar") + # or "line"
   theme(axis.text.x = element_text(angle =60, hjust = 1))+
  ggtitle("Total Sale Price in Each Neighborhood")
```

```{r}
ggplot(data = Manhattan,
  aes(NEIGHBORHOOD., SALE.PRICE.)) +
  scale_y_continuous(labels = comma)+
  stat_summary(fun.y = median, # adds up all observations for the month
    geom = "bar") + 
   theme(axis.text.x = element_text(angle =60, hjust = 1))+
  ggtitle("Median Sale Price in Each Neighborhood")
```

```{r}
ggplot(data = Manhattan,
  aes(NEIGHBORHOOD., SALE.PRICE.)) +
  scale_y_continuous(labels = comma)+
  stat_summary(fun.y = mean, # adds up all observations for the month
    geom = "bar") + 
   theme(axis.text.x = element_text(angle =60, hjust = 1))+
  ggtitle("Mean Sale Price in Each Neighborhood")
```

```{r}
ggplot(data = Midtown,
  aes(Month, fill = NEIGHBORHOOD.)) +
   theme(axis.text.x = element_text(angle =60, hjust = 1))+
   geom_bar(position = "dodge")+
  ggtitle("Property Sale in Midtown")
```

```{r}

p <-  Midtown%>%
  filter(SALE.PRICE.<2210000000) %>% ggplot( aes(GROSS.SQUARE.FEET., SALE.PRICE., size = SALE.PRICE., color=NEIGHBORHOOD.)) +
  geom_point() +
  scale_y_continuous(labels = comma)+
    theme_bw()+
  ggtitle("Sale Price based on Gross square feet in each Neighborhood")
p
```

```{r}
gf <-  Midtown%>%
  filter(SALE.PRICE.<2210000000) %>% ggplot( aes(LAND.SQUARE.FEET., SALE.PRICE., size = SALE.PRICE., color=NEIGHBORHOOD.)) +
  geom_point() +
  scale_y_continuous(labels = comma)+
    theme_bw()+
  ggtitle("Sale Price based on Land square feet in each Neighborhood")
gf
```

```{r}
ggplot(Manhattan)+aes(x=YEAR.BUILT.,y=log(SALE.PRICE.))+geom_point()
```


```{r}
B <- ggplot(data = Midtown,aes(x=log(SALE.PRICE.),fill = NEIGHBORHOOD.))+
  geom_histogram()+
  ggtitle("Log Sale Prices Based on Location")
B
```

```{r}
C <- ggplot(data = Midtown,aes(x=log(SALE.PRICE.),fill = BUILDING.CLASS.AT.TIME.OF.SALE.))+
  geom_histogram()+
  ggtitle("Log Sale Prices Based on Building Class")
C
```
```{r}
data("zipcode")
colnames(Manhattan)[3] <- "zip"
Manhattan$zip <- as.character(Manhattan$zip)
Manhattan_zip <- inner_join(Manhattan,zipcode,by="zip")
Manhattan_zip$latitude <- as.numeric(Manhattan_zip$latitude)
Manhattan_zip$longitude <- as.numeric(Manhattan_zip$longitude)
Ne_sum <- aggregate(SALE.PRICE.~NEIGHBORHOOD.,data = Manhattan_zip,sum)

ASDF <- inner_join(Ne_sum, Manhattan_zip,by = "NEIGHBORHOOD.")
ASDF <- distinct(ASDF,NEIGHBORHOOD.,.keep_all = TRUE)

# m <- leaflet(data =ASDF ) %>%
#   addTiles() %>%  # Add default OpenStreetMap map tiles
#   addMarkers( ~longitude,~latitude
# , popup = ~as.character(SALE.PRICE..x), label = ~as.character(NEIGHBORHOOD.))
# m  # Print the map
```

```{r,scale=2,warning=FALSE}
img_path1 <- "Capture.PNG"
img1 <- readPNG(img_path1, native = TRUE, info = TRUE)
# Small fig.width
include_graphics(img_path1)
```
# Benford Law Analysis
```{r}
####### Benford analysis
bfd <- benford(Manhattan$SALE.PRICE.)
plot(bfd)
```
The original data is in dark color and the expected frequency are the red dash line. From the plot, we found that the first digits indicate the most data have a tendency to follows Benford's distribution. The digits distribution of second order test shows that there is a clear discrepancy around 50.

Then, I print the main results of the analysis:

```{r}
bfd
```
The numbers of Mantissa from summary are Mean as 0.542, Var as 0.095, Ex.Kurtosis are -1.331, and Skewness are -0.222, which are close to expect value.
Degree of freedom equals 89 and p-value is small enough that we are supposed to reject the benford's law. However, thinking of reality, price start with two digits of 99 or 89 are acceptable. 
```{r}
suspects <- getSuspects(bfd, Manhattan)
suspects
```


```{r}
manhattan_price <- getBfd(benford(Manhattan$SALE.PRICE.))
kable(manhattan_price)
kable(head(suspectsTable(benford(Manhattan$SALE.PRICE.)),10))
```
# Conclusion

By looking at the five output result for Benford's law, it looks like that they are following Benford distribution. Although there are some deviation for some digits, but it may be due to some marketing strategy. Therefore, I think this dataset for sale price are good to trust. 

